---
title: "Week10_hw"
format: pdf
editor: visual
---

## Week 10_hw

1.  Use code chunk options eval, include, echo, results, dependson in at least one code chunk to illustrate your knowledge and mastery of the code chunk options.

    \# A code chunk with include = FALSE was used to upload packages but not present any code and results

    ```{r, include=FALSE}
    library(ggplot2)
    library(psych)
    ```

    \# This is an analysis code chunk with eval = FALSE. We used it to show the simple way to explore the relationship between two variables in mtcars without executing it.

    ```{r, eval=FALSE}
    plot(mtcars$wt, mtcars$mpg, 
         xlab = "Weight", ylab = "Miles Per Gallon",
         main = "Scatter plot of mpg vs. wt")
    ```

    \# This is an analysis code chunk with results = "hide".

    ```{r, results='hide'}
    summary(mtcars)
    ```

    #This is an analysis code chunk with echo=FALSE, as I only want to see the Scatterplot without showing code in the presentation

    ```{r, echo=FALSE}
    plot(mtcars$wt, mtcars$mpg, 
         xlab = "Weight", ylab = "Miles Per Gallon",
         main = "Scatter plot of mpg vs. wt")
    ```

    setup data

    ```{r, setup}
    data <- c(1, 2, 3, 4, 5)
    ```

    \# This is an analysis code chunk with dependson, so the current code chunk depends on the results from another code chunk as specified.

    ```{r, dependson='setup'}
    mean(data)
    ```

```{=html}
<!-- -->
```
2.  Pick one new code chunk not discussed in the book and describe and illustrate how to use it.

    \# This is an analysis code chunk with fig.width and fig.height. This is very useful for consistency in gene differential expression visualization to Set the width and height of figures, respectively.

    ```{r, fig.width=5, fig.height=5}
    plot(mtcars$wt, mtcars$mpg, 
         xlab = "Weight", ylab = "Miles Per Gallon",
         main = "Scatter plot of mpg vs. wt")
    ```

```{=html}
<!-- -->
```
3.  Save an object with save()

    ```{r}
    # The previous setup data has been saved here.
    save(data, file = "data.RData")
    ```

4.  Save an R script and load it in a new code chunk.

    ```{r, include=TRUE}
    # Run main analysis
    source("scatter.R")
    ```

5.  Write one statement using the inline static code "\\texttt" and with \\verb

    texttt{This is week 10 homework}.

    \\verb\|\\\\texttt\|. 

    \\verb\|Look at this example.\|
